---
title: "Project Proposal"
output:
  html_document: default
  pdf_document: default
---

__Proposal Deadline: Feb 3, 2019 23:59:00 hrs.__

- Edit this markdown file by __replacing only__ what is there in the
chunks named `q0`, `q1`, `q2`, ..., `q5` with your team's appropriate
answers. These chunks have been filled in as an example using the
OpenFDA data.

- Upload the filled in markdown to the project proposal assignment
area (will be created shortly) in every one of the team member's
private directory with the name `proposal.Rmd`.

0. Who are the authors of this package? See format below where you
   should replace `sunet1`, `sunet2`, and `Full Name1` and `Full
   Name2`.

```{r q0}
authors <- list(dcom99 = "Douglas H Comstock",
                bag9031 = "Balagopal Gopakumar")
```

1. What is your package trying to achieve?  Who is it aimed at?

```{r,q1, eval=FALSE}

We will be pursuing the "Weather Data" project. 

1.  Our package will simplify the process of querying and collecting of weather data 
    around specific regions directly from the web. 

2. Analysis will then be possible on the collected and cleaned information.

3. Visualization: Possibly a nice GUI and output via shiny, time permitting.

Audience: There can be two potential users of this package: 
  (1) Data scientists/analysts, who are interested in obtain weather related information
      for analysis 
  (2) A non- analytical audience, who could user a user interface (GUI) for the library
      to track and obtain useful information for a specific region.

```

2. Briefly describe the background if that's not obvious.  What field
   or area of interest is it related to?  (Just briefly, in a paragraph
   or two, maximum.) References, including web references, are welcome
   where available.

```{r,q2, eval=FALSE}

The three main phases for the project will be 
(1) accessing and retrieving weather related information from openweathermap.org, 
minimizing the workload for the user; 
(2) data munging - enabling the retrieved information to be utilized for visualization and 
future pipelines; 
(3) visualization/communicating the weather related data to the users.

```

3. Provide one or two use cases; that is, in a sentence or so say how
   you see someone using the package.

```{r,q3, eval=FALSE}

- Data scientists/analysts could use this library to obtain weather information for a 
  specific city/zipcode and the personal weather stations within a certain radius, 
  then download and work with the data.
- Users (non analysts) can use the package interface to view the weather patterns, 
  or simply the current data and forecast for their specified area.


```

4. If you can, list the main functions or other software you plan on
   including.  No need to implement anything now, but you should have
   an idea.

```{r, q4, eval=FALSE}

The R package will provide the following functions: 
  
  Requirements specified
  1. Query : (a) API interface; (b) webscape additional data using rvest package
  
  Extensions proposed
  1. Comparison module: Enable users to bring in historical data and perform comparison 
  of current weather patterns. Ideally, this would be a dashboard type interface (R Shiny?)
  2. ChangePoint detection: Detecting periods in the past when there was a significant 
  change in temperature/precipitation (based on user preference). This will essentially be a matter
  of finding and reporting inflection points to answer "when did the current trend begin?".

```

```{r, echo = FALSE, hide = FALSE}
## Do not edit
none <- "none"
basic <- "basic"
proficient <- "proficient"
dangerous <- "dangerous :-)"
```

5. For languages C/C++, Java, Python, Ruby, please specify your
   proficiency: Proficient, basic knowledge, no knowledge.  (This
   helps us evaluate the proposal sometimes and offer suggestions.)

```{r q5}
languages <- list(
    ## replace the sunet1 and sunet2 as you did above and edit
    ## appropriately for each member
    'Douglas H Comstock' = c(cxx = none,
               java = none,
               python = basic,
               julia = none, 
               ruby = none)
    ,
    'Balagopal Gopakumar' = c(cxx = basic,
               java = none,
               python = proficient,
               julia = none,                
               ruby = none)
)
```

## Comments and Responses

__Note__ Your responses should be in this markdown itself, right after
each point. You do not need to submit or email the responses, but do
update it on your github repo exactly where you found it.

Since you are doing one of the suggested projects, comments are minimal.

1. Many sites throttle API requests if you are not a paying customer.

2. Your definition of changepoint is not clear. How would the user
   describe the "change"? Is it just a difference, a range?

3. Always ensure I can run examples locally without having to get on
   the web.












